#My First Notebook
This notebook is basically just me trying to see how this stuff works. So let's see.
```{r}
silence<-suppressWarnings
silence(library(tidyverse))
silence(library(reshape2))
silence(library(modelr))
silence(library(lubridate))
UAdaily<-flights %>% 
  filter(carrier=="UA") %>% 
  mutate(date=make_date(year,month,day)) %>% 
  select(-year,-month,-day,-time_hour) %>% 
  group_by(date) %>% 
  summarise(n=n())

```
Ok Now Let's Visualise how the distribution of UA fligths throughtout the year.
```{r}
ggplot(UAdaily,aes(date,n))+geom_line()
```

How about we see the daily distribution of flights?
```{r}
UAdaily<-UAdaily %>% 
  mutate(wday=wday(date,label=TRUE)) 
  ggplot(UAdaily,aes(wday,n))+geom_boxplot()
```

_The flight distribution seems to be concentrated in week days. Saturday seems to have the lowest number of flights. Let's model and visualise it_
```{r}
modUA<-lm(n~wday,data=UAdaily)
UAgrid<-UAdaily %>% 
  data_grid(wday) %>% 
  add_predictions(modUA,"n")
ggplot(UAdaily,aes(wday,n))+geom_boxplot()+
  geom_point(data=UAgrid,colour="red",shape=6,size=3)
summary(modUA)
```
Next we add residuals to try and remove our pattern.
```{r}
 UAdaily<-UAdaily %>% 
  add_residuals(modUA,"resid")
  ggplot(UAdaily,aes(date,resid,color=wday))+geom_ref_line(h=0)+geom_line()+
    ggtitle("Pattern of flight Distributions")+theme(plot.title = element_text(hjust=0.5))
```
Then what next? We see the pattern isn different towards the end of the year. For better visualisation we extract more.
```{r}
ggplot(UAdaily,aes(date,resid))+geom_ref_line(h=0)+geom_line(colour="grey45")+
  geom_smooth(se=FALSE,span=0.20)+ggtitle("Residual Distribution")+theme(plot.title=element_text(hjust=0.5))
```
There are less flights towards the end of the year. 
```{r}
UAdaily %>% 
  filter(wday=="Sat") %>% 
  ggplot(aes(date,n))+geom_point()+geom_line()+scale_x_date(NULL,date_breaks = "1 month",date_labels = "%b")+ggtitle("Flight Distributions over the Course of the Year")+
  theme(plot.title=element_text(hjust=0.5))

```

