
```{r}
silence<-suppressWarnings
silence(library(tidyverse))
silence(library(reshape2))
silence(library(GGally))
silence(library(modelr))
silence(library(forcats))
silence(library(hexbin))
```
In this notebook, I'll do some practice. Take note of the difference between NA and NULL.
```{r}
gapminder %>%
  group_by(continent) %>%
  filter(!continent=="Oceania") %>% 
  ggplot(aes(year, lifeExp, fill = continent)) +
  geom_bar(stat = "identity", position = position_identity()) +
  labs(title = "Variation of Life Expectancy over the Years") + theme(
  plot.title = element_text(hjust = 0.5),
  panel.grid = element_blank(),
  panel.background = element_blank(),
  panel.border=element_rect(fill=NA)
  )
  
```
We notice a rather ambiguous trend in Africa. We'll focus on Africa. There has however been an increase in gdp over the years. So how do we explain the life Expectancy?
```{r}
     gapminder %>% 
     filter(country=="Nigeria") %>% 
     mutate(gdp=gdpPercap*pop) %>% 
   ggplot(aes(year,gdp))+geom_point()
          

      
```
There clearly is a steady increase in gdp in Nigeria. How has this correlated with lifeExp?
```{r}
  Nigeria<-gapminder %>% 
            mutate(gdp=gdpPercap*pop) %>% 
          filter(country=="Nigeria")
 gapminder %>% 
            mutate(gdp=gdpPercap*pop) %>% 
          filter(country=="Nigeria") %>% 
         ggplot(aes(year,lifeExp))+geom_point()
  
        
           
         
     

```
The general trend is an increase in gdp correlating to an increase in lifeExp except between 1980 and 2000. We attempt to model lifeExp and gdp.
```{r}
    fitNigeria<-lm(lifeExp~gdp,data=Nigeria)
   summary(fitNigeria)
```


The summary statistics of our model suggest a correlation between lifeExp and gdp. We proceed to apply the model.
```{r}
  Nigeriagrid<-Nigeria %>%
               data_grid(gdp) %>% 
              add_predictions(fitNigeria,"lifeExp")
  ggplot(Nigeria,aes(gdp,lifeExp))+geom_point()+geom_smooth(data=fitNigeria,colour="red")
```
Let's examine how much our model differs from the original dataset.
```{r}
 Nigeria<-Nigeria %>% 
         add_residuals(fitNigeria,"resid")
ggplot(Nigeria,aes(year,resid,colour=gdp))+geom_point()
```
A good model should have the residuals randomly distributed around zero. Does our model appear to be fit enough? Seems not to be a good model.
